---
title: "project"
output: html_document
date: "2023-11-26"
---

```{r pressure, echo=FALSE}
library(FinTS)
library(fGarch)
library(rugarch)
library(forecast)
library(ggplot2)
library(lmtest)
library(tseries)
daily <- read.csv("2318.HK.csv", header = TRUE)
daily$Date <- as.Date(daily$Date)
daily$Adj.Close <- as.numeric(daily$Adj.Close) 
daily_data <- daily[1526:2466,c(1,6)]
daily_data <- na.omit(daily_data)
```

```{r pressure, echo=FALSE}
plot(daily_data,type = "l")
```
```{r pressure, echo=FALSE}
d_return <- data.frame(Date = daily_data[,1][-1], return = diff(daily_data[,2]) / daily_data[-
dim(daily_data)[1], 2]) 

d_lreturn <- data.frame(Date = daily_data[,1][-1], logreturn = log(d_return[,2] + 1))

d_return$return <- 100 * d_return$return # 乘以100(%)作为分析数据
d_lreturn$logreturn <- 100 * d_lreturn$logreturn # 乘以100(%)作为分析数据

plot(d_lreturn$logreturn,type="l")
```

```{r pressure, echo=FALSE}
acf(d_lreturn$logreturn)
pacf(d_lreturn$logreturn)
```



```{r pressure, echo=FALSE}
Box.test(d_lreturn[,2], lag = 12, type = "Ljung")
```
```{r pressure, echo=FALSE}
ARMA_dlr_fit1 <- auto.arima(d_lreturn[,2],start.p = 0, max.p = 2, start.q = 0,
max.q = 2, stepwise = FALSE, ic = "aic", trace = T) # AIC信息准则下的最优模型是总体均值为0的ARMA(0,0)
ARMA_dlr_fit2 <- auto.arima(d_lreturn[,2],start.p = 0, max.p = 2, start.q = 0,
max.q = 2, stepwise = FALSE, ic = "bic", trace = T) # BIC信息准则下的最优模型是总体均值为0的ARMA(0,0)
ARMA_dlr_fit3 <- auto.arima(d_lreturn[,2],start.p = 0, max.p = 2, start.q = 0,
max.q = 2, stepwise = FALSE, ic = "aicc", trace = T) # AICc信息准则下的最优模型是总体均值为0的ARMA(0,0)
```


```{r pressure, echo=FALSE}
# GARCH
Box.test((d_lreturn[,2])^2, lag = 12, type = "Ljung")
```

```{r pressure, echo=FALSE}
plot((d_lreturn[,2])^2,type = "l")
```

```{r pressure, echo=FALSE}
acf((d_lreturn[,2])^2)
```

```{r pressure, echo=FALSE}
pacf((d_lreturn[,2])^2)
```

```{r pressure, echo=FALSE}
ArchTest(d_lreturn[,2],lags=12)
```

```{r pressure, echo=FALSE}
# 拟合条件扰动为正态分布且不含均值项的GARCH(p,q)模型，p,q最大值均为2
GARCH_dlr_fit1 <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
GARCH_dlr_fit2 <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
GARCH_dlr_fit3 <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
GARCH_dlr_fit4 <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
GARCH_dlr_fit5 <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
GARCH_dlr_fit6 <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "norm", include.mean = FALSE)
# 拟合条件扰动为正态分布且含有均值项的GARCH(p,q)模型，p,q最大值均为2
GARCH_dlr_fit7 <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "norm")
GARCH_dlr_fit8 <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "norm")
GARCH_dlr_fit9 <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "norm")
GARCH_dlr_fit10 <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "norm")
GARCH_dlr_fit11 <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "norm")
GARCH_dlr_fit12 <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "norm")

GARCH_dlr_ICs_norm <-  rbind(GARCH_dlr_fit1@fit$ics, GARCH_dlr_fit2@fit$ics, GARCH_dlr_fit3@fit$ics, GARCH_dlr_fit4@fit$ics, GARCH_dlr_fit5@fit$ics, GARCH_dlr_fit6@fit$ics, GARCH_dlr_fit7@fit$ics, GARCH_dlr_fit8@fit$ics, GARCH_dlr_fit9@fit$ics, GARCH_dlr_fit10@fit$ics, GARCH_dlr_fit11@fit$ics, GARCH_dlr_fit12@fit$ics)
```

```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(GARCH_dlr_ICs_norm[1,], type = "b", pch = 16, col = "burlywood", xlab = "Criterion", ylab = "value", ylim = c(min(GARCH_dlr_ICs_norm), max(GARCH_dlr_ICs_norm)), main = "Information Criteria of GARCH(norm)", xaxt = "n")
lines(GARCH_dlr_ICs_norm[2, ], type = "b", pch = 16, col = "firebrick")
lines(GARCH_dlr_ICs_norm[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(GARCH_dlr_ICs_norm[4,], type = "b", pch = 16, col = "powderblue")
lines(GARCH_dlr_ICs_norm[5,], type = "b", pch = 16, col = "palegreen")
lines(GARCH_dlr_ICs_norm[6,], type = "b", pch = 16, col = "pink")
lines(GARCH_dlr_ICs_norm[7,], type = "b", pch = 16, col = "orchid")
lines(GARCH_dlr_ICs_norm[8,], type = "b", pch = 16, col = "lightsalmon")
lines(GARCH_dlr_ICs_norm[9,], type = "b", pch = 16, col = "royalblue")
lines(GARCH_dlr_ICs_norm[10,], type = "b", pch = 16, col = "lightslategrey")
lines(GARCH_dlr_ICs_norm[11,], type = "b", pch = 16, col = "palevioletred")
lines(GARCH_dlr_ICs_norm[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(GARCH_dlr_ICs_norm[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(GARCH_dlr_ICs_norm[1,]) + 0.3
legend_y <- mean(range(GARCH_dlr_ICs_norm)) +0.08

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8","9","10","11","12"), col = c("burlywood", "firebrick", "mediumseagreen", "powderblue","palegreen","pink","orchid","lightsalmon","royalblue","lightslategrey","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```

```{r pressure, echo=FALSE}
# 拟合条件扰动为std分布且不含均值项的GARCH(p,q)模型，p,q最大值均为2
GARCH_dlr_fit1_s <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
GARCH_dlr_fit2_s <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
GARCH_dlr_fit3_s <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
GARCH_dlr_fit4_s <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
GARCH_dlr_fit5_s <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
GARCH_dlr_fit6_s <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
# 拟合条件扰动为std分布且含有均值项的GARCH(p,q)模型，p,q最大值均为2
GARCH_dlr_fit7_s <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit8_s <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit9_s <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit10_s <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit11_s <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit12_s <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "std")

GARCH_dlr_ICs_std <-  rbind(GARCH_dlr_fit1_s@fit$ics, GARCH_dlr_fit2_s@fit$ics, GARCH_dlr_fit3_s@fit$ics, GARCH_dlr_fit4_s@fit$ics, GARCH_dlr_fit5_s@fit$ics, GARCH_dlr_fit6_s@fit$ics, GARCH_dlr_fit7_s@fit$ics, GARCH_dlr_fit8_s@fit$ics, GARCH_dlr_fit9_s@fit$ics, GARCH_dlr_fit10_s@fit$ics, GARCH_dlr_fit11_s@fit$ics, GARCH_dlr_fit12_s@fit$ics)
```

```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(GARCH_dlr_ICs_std[1,], type = "b", pch = 16, col = "burlywood", xlab = "Criterion", ylab = "value", ylim = c(min(GARCH_dlr_ICs_std), max(GARCH_dlr_ICs_std)), main = "Information Criteria of GARCH(std)", xaxt = "n")
lines(GARCH_dlr_ICs_std[2, ], type = "b", pch = 16, col = "firebrick")
lines(GARCH_dlr_ICs_std[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(GARCH_dlr_ICs_std[4,], type = "b", pch = 16, col = "powderblue")
lines(GARCH_dlr_ICs_std[5,], type = "b", pch = 16, col = "palegreen")
lines(GARCH_dlr_ICs_std[6,], type = "b", pch = 16, col = "pink")
lines(GARCH_dlr_ICs_std[7,], type = "b", pch = 16, col = "orchid")
lines(GARCH_dlr_ICs_std[8,], type = "b", pch = 16, col = "lightsalmon")
lines(GARCH_dlr_ICs_std[9,], type = "b", pch = 16, col = "royalblue")
lines(GARCH_dlr_ICs_std[10,], type = "b", pch = 16, col = "lightslategrey")
lines(GARCH_dlr_ICs_std[11,], type = "b", pch = 16, col = "palevioletred")
lines(GARCH_dlr_ICs_std[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(GARCH_dlr_ICs_std[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(GARCH_dlr_ICs_std[1,]) + 0.3
legend_y <- mean(range(GARCH_dlr_ICs_std)) +0.06

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8","9","10","11","12"), col = c("burlywood", "firebrick", "mediumseagreen", "powderblue","palegreen","pink","orchid","lightsalmon","royalblue","lightslategrey","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```

GARCH_dlr_fit8_S garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "std")
GARCH_dlr_fit2_s garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "std", include.mean = FALSE)
red)


```{r pressure, echo=FALSE}
# 拟合条件扰动为ged分布且不含均值项的GARCH(p,q)模型，p,q最大值均为2
# GARCH_dlr_fit1 <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
GARCH_dlr_fit2_g <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
GARCH_dlr_fit3_g <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
#GARCH_dlr_fit4 <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
GARCH_dlr_fit5_g <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
GARCH_dlr_fit6_g <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
# 拟合条件扰动为正态分布且含有均值项的GARCH(p,q)模型，p,q最大值均为2
#GARCH_dlr_fit7 <- garchFit(~garch(1,0), d_lreturn[,2], cond.dist = "ged")
GARCH_dlr_fit8_g <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "ged")
GARCH_dlr_fit9_g <- garchFit(~garch(1,2), d_lreturn[,2], cond.dist = "ged")
#GARCH_dlr_fit10 <- garchFit(~garch(2,0), d_lreturn[,2], cond.dist = "ged")
GARCH_dlr_fit11_g <- garchFit(~garch(2,1), d_lreturn[,2], cond.dist = "ged")
GARCH_dlr_fit12_g <- garchFit(~garch(2,2), d_lreturn[,2], cond.dist = "ged")

GARCH_dlr_ICs_ged <-  rbind(10, GARCH_dlr_fit2_g@fit$ics, GARCH_dlr_fit3_g@fit$ics, 10, GARCH_dlr_fit5_g@fit$ics, GARCH_dlr_fit6_g@fit$ics, 10, GARCH_dlr_fit8_g@fit$ics, GARCH_dlr_fit9_g@fit$ics, 10, GARCH_dlr_fit11_g@fit$ics, GARCH_dlr_fit12_g@fit$ics)
```

GARCH_dlr_fit2_g <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "ged", include.mean = FALSE)
GARCH_dlr_fit8_g <- garchFit(~garch(1,1), d_lreturn[,2], cond.dist = "ged")
```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(GARCH_dlr_ICs_ged[2,], type = "b", pch = 16, col = "firebrick", xlab = "Criterion", ylab = "value", ylim = c(min(GARCH_dlr_ICs_ged), 4.293), main = "Information Criteria of GARCH(ged)", xaxt = "n")
lines(GARCH_dlr_ICs_ged[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(GARCH_dlr_ICs_ged[5,], type = "b", pch = 16, col = "palegreen")
lines(GARCH_dlr_ICs_ged[6,], type = "b", pch = 16, col = "pink")
lines(GARCH_dlr_ICs_ged[8,], type = "b", pch = 16, col = "lightsalmon")
lines(GARCH_dlr_ICs_ged[9,], type = "b", pch = 16, col = "royalblue")
lines(GARCH_dlr_ICs_ged[11,], type = "b", pch = 16, col = "palevioletred")
lines(GARCH_dlr_ICs_ged[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(GARCH_dlr_ICs_ged[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(GARCH_dlr_ICs_ged[1,]) + 0.3
legend_y <- mean(range(GARCH_dlr_ICs_ged)) +0.01

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8"), col = c( "firebrick", "mediumseagreen","palegreen","pink","lightsalmon","royalblue","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```
```{r pressure, echo=FALSE}
fit1_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit2_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit3_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit4_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit5_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit6_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit7_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit8_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit9_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit10_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit11_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 2)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])


sGARCH_dlr_ICs <-  cbind(infocriteria(fit1_s),infocriteria(fit2_s),infocriteria(fit3_s),infocriteria(fit4_s),infocriteria(fit5_s),infocriteria(fit6_s),infocriteria(fit7_s),infocriteria(fit8_s),infocriteria(fit9_s),infocriteria(fit10_s),infocriteria(fit11_s),infocriteria(fit12_s))
sGARCH_dlr_ICs <- t(sGARCH_dlr_ICs)
```


```{r pressure, echo=FALSE}
fit1_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 1)),
  distribution.model = "std"), data = d_lreturn[,2])
fit2_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(1, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit3_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(2, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit4_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(3, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit5_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(4, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit7_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit8_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(1, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit9_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(2, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit10_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(3, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit11_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(4, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 0)),
  distribution.model = "std"), data = d_lreturn[,2])


sGARCH_dlr_ICs <-  cbind(infocriteria(fit1_s),infocriteria(fit2_s),infocriteria(fit3_s),infocriteria(fit4_s),infocriteria(fit5_s),infocriteria(fit6_s),infocriteria(fit7_s),infocriteria(fit8_s),infocriteria(fit9_s),infocriteria(fit10_s),infocriteria(fit11_s),infocriteria(fit12_s))
sGARCH_dlr_ICs <- t(sGARCH_dlr_ICs)
```


fit2_s <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(sGARCH_dlr_ICs[1,], type = "b", pch = 16, col = "burlywood", xlab = "Criterion", ylab = "value", ylim = c(min(sGARCH_dlr_ICs), max(GARCH_dlr_ICs_norm)), main = "Information Criteria of sGARCH", xaxt = "n")
lines(sGARCH_dlr_ICs[2, ], type = "b", pch = 16, col = "firebrick")
lines(GARCH_dlr_ICs_norm[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(GARCH_dlr_ICs_norm[4,], type = "b", pch = 16, col = "powderblue")
lines(GARCH_dlr_ICs_norm[5,], type = "b", pch = 16, col = "palegreen")
lines(GARCH_dlr_ICs_norm[6,], type = "b", pch = 16, col = "pink")
lines(GARCH_dlr_ICs_norm[7,], type = "b", pch = 16, col = "orchid")
lines(GARCH_dlr_ICs_norm[8,], type = "b", pch = 16, col = "lightsalmon")
lines(GARCH_dlr_ICs_norm[9,], type = "b", pch = 16, col = "royalblue")
lines(GARCH_dlr_ICs_norm[10,], type = "b", pch = 16, col = "lightslategrey")
lines(GARCH_dlr_ICs_norm[11,], type = "b", pch = 16, col = "palevioletred")
lines(GARCH_dlr_ICs_norm[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(GARCH_dlr_ICs_norm[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(GARCH_dlr_ICs_norm[1,]) + 0.3
legend_y <- mean(range(GARCH_dlr_ICs_norm)) +0.08

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8","9","10","11","12"), col = c("burlywood", "firebrick", "mediumseagreen", "powderblue","palegreen","pink","orchid","lightsalmon","royalblue","lightslategrey","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```

```{r pressure, echo=FALSE}
fit2_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit3_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 2)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit5_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(2, 1)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit6_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(2, 2)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit8_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit9_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 2)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit11_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(2, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(2, 2)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])


iGARCH_dlr_ICs <-  cbind(10,infocriteria(fit2_i),infocriteria(fit3_i),10,infocriteria(fit5_i),infocriteria(fit6_i),10,infocriteria(fit8_i),infocriteria(fit9_i),10,infocriteria(fit11_i),infocriteria(fit12_i))
iGARCH_dlr_ICs <- t(iGARCH_dlr_ICs)
```

fit8_i <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(iGARCH_dlr_ICs[2,], type = "b", pch = 16, col = "firebrick", xlab = "Criterion", ylab = "value", ylim = c(min(iGARCH_dlr_ICs), 4.27), main = "Information Criteria of iGARCH", xaxt = "n")
lines(iGARCH_dlr_ICs[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(iGARCH_dlr_ICs[5,], type = "b", pch = 16, col = "palegreen")
lines(iGARCH_dlr_ICs[6,], type = "b", pch = 16, col = "pink")
lines(iGARCH_dlr_ICs[8,], type = "b", pch = 16, col = "lightsalmon")
lines(iGARCH_dlr_ICs[9,], type = "b", pch = 16, col = "royalblue")
lines(iGARCH_dlr_ICs[11,], type = "b", pch = 16, col = "palevioletred")
lines(iGARCH_dlr_ICs[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(iGARCH_dlr_ICs[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(iGARCH_dlr_ICs[1,]) + 0.3
legend_y <- mean(range(iGARCH_dlr_ICs)) +0.01

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8"), col = c( "firebrick", "mediumseagreen","palegreen","pink","lightsalmon","royalblue","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```
```{r pressure, echo=FALSE}
fit2_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit3_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 2)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit5_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(2, 1)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit6_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(2, 2)),
  mean.model = list(armaOrder = c(0, 0),include.mean = FALSE),
  distribution.model = "std"), data = d_lreturn[,2])
fit8_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit9_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 2)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit11_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(2, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(2, 2)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])

eGARCH_dlr_ICs <-  cbind(10,infocriteria(fit2_e),infocriteria(fit3_e),10,infocriteria(fit5_e),infocriteria(fit6_e),10,infocriteria(fit8_e),infocriteria(fit9_e),10,infocriteria(fit11_e),infocriteria(fit12_e))
eGARCH_dlr_ICs <- t(eGARCH_dlr_ICs)
```

fit8_e <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(eGARCH_dlr_ICs[2,], type = "b", pch = 16, col = "firebrick", xlab = "Criterion", ylab = "value", ylim = c(min(eGARCH_dlr_ICs), 4.285), main = "Information Criteria of eGARCH", xaxt = "n")
lines(eGARCH_dlr_ICs[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(eGARCH_dlr_ICs[5,], type = "b", pch = 16, col = "palegreen")
lines(eGARCH_dlr_ICs[6,], type = "b", pch = 16, col = "pink")
lines(eGARCH_dlr_ICs[8,], type = "b", pch = 16, col = "lightsalmon")
lines(eGARCH_dlr_ICs[9,], type = "b", pch = 16, col = "royalblue")
lines(eGARCH_dlr_ICs[11,], type = "b", pch = 16, col = "palevioletred")
lines(eGARCH_dlr_ICs[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(eGARCH_dlr_ICs[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(eGARCH_dlr_ICs[1,]) + 0.3
legend_y <- mean(range(eGARCH_dlr_ICs)) +0.01

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8"), col = c( "firebrick", "mediumseagreen","palegreen","pink","lightsalmon","royalblue","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```

```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")
ICs <- rbind(GARCH_dlr_ICs_norm[2,],GARCH_dlr_ICs_std[2, ],GARCH_dlr_ICs_std[8, ],GARCH_dlr_ICs_ged[2, ],GARCH_dlr_ICs_ged[8,],sGARCH_dlr_ICs[2,],iGARCH_dlr_ICs[8,],eGARCH_dlr_ICs[8,])
# Increase margin space for the plot
par(mar = c(5, 6, 4, 8))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(ICs[1,], type = "b", pch = 16, col = "firebrick", xlab = "Criterion", ylab = "value", ylim = c(min(ICs), max(ICs)), main = "Information Criteria of best models", xaxt = "n")
lines(ICs[2, ], type = "b", pch = 16, col = "mediumseagreen")
lines(ICs[3,], type = "b", pch = 16, col = "palegreen")
lines(ICs[4,], type = "b", pch = 16, col = "pink")
lines(ICs[5,], type = "b", pch = 16, col = "lightsalmon")
lines(ICs[6,], type = "b", pch = 16, col = "royalblue")
lines(ICs[7,], type = "b", pch = 16, col = "palevioletred")
lines(ICs[8,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(ICs[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(ICs[1,]) + 0.3
legend_y <- mean(range(ICs)) +0.05

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("1", "2", "3", "4","5","6","7","8"), col = c( "firebrick", "mediumseagreen","palegreen","pink","lightsalmon","royalblue","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```
eGARCH_dlr_ICs[8,]
```{r pressure, echo=FALSE}
# model checking
# ARMA(0,0) + iGARCH(1,1)
# standardize residual
## compute standardize residual
show(fit9_a)
res_dlr <- residuals(fit9_a, standardize=TRUE)
## Box-Ljung test of standardize residual
Box.test(res_dlr, lag = 12, type = "Ljung")    # lag = 12
## TS plot of standardize residual
plot(res_dlr, type = "l", main = "TS plot of standardize residual")
```

```{r pressure, echo=FALSE}
par(mfrow=c(1,2))
## ACF of standardize residual
acf(res_dlr, main = "ACF of standardize residual")
## PACF of standardize residual
pacf(res_dlr, main = "PACF of standardize residual")
```

```{r pressure, echo=FALSE}
# squared standardize residual
## Box-Ljung test of squared standardize residual
Box.test(res_dlr^2, lag = 12, type = "Ljung")    # lag = 12
## TS plot of squared standardize residual
plot(res_dlr^2, type = "l", main = "TS plot of squared standardize residual")
```

```{r pressure, echo=FALSE}
par(mfrow=c(1,2))
## ACF of squared standardize res
acf(res_dlr^2, main = "ACF of squared standardize res")
## PACF of squared st
pacf(res_dlr^2, main = "PACF of squared standardize res")
## LM Arch test of squared standardize res
ArchTest(res_dlr,lags=12)
```

```{r pressure, echo=FALSE}
#12
fit1_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std",fixed.pars = list(mu=0,ar2=0,ar3=0,ar4=0,ar5=0,omega=0)), data = d_lreturn[,2])
fit2_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 4)),
  distribution.model = "std"), data = d_lreturn[,2])
fit3_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(2, 2)),
  distribution.model = "std"), data = d_lreturn[,2])
fit4_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit5_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit6_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 4)),
  distribution.model = "std"), data = d_lreturn[,2])
fit7_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(2, 2)),
  distribution.model = "std"), data = d_lreturn[,2])
fit8_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit9_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0)),
  distribution.model = "std"), data = d_lreturn[,2])
fit10_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 4)),
  distribution.model = "std"), data = d_lreturn[,2])
fit11_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(2, 2)),
  distribution.model = "std"), data = d_lreturn[,2])
fit12_a <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(5, 0)),
  distribution.model = "std"), data = d_lreturn[,2])


allGARCH_dlr_ICs <-  cbind(infocriteria(fit1_a),infocriteria(fit2_a),infocriteria(fit3_a),infocriteria(fit4_a),infocriteria(fit5_a),infocriteria(fit6_a),infocriteria(fit7_a),infocriteria(fit8_a),infocriteria(fit9_a),infocriteria(fit10_a),infocriteria(fit11_a),infocriteria(fit12_a))
allGARCH_dlr_ICs <- t(allGARCH_dlr_ICs)
```

```{r pressure, echo=FALSE}
x_label <- c("AIC", "BIC", "SIC", "HQIC")

# Increase margin space for the plot
par(mar = c(5, 6, 4, 13))

plot.new()

# Plot the chart with swapped x-axis and y-axis
plot(allGARCH_dlr_ICs[1,], type = "b", pch = 16, col = "burlywood", xlab = "Criterion", ylab = "value", ylim = c(min(allGARCH_dlr_ICs), max(allGARCH_dlr_ICs)), main = "Information Criteria of all GARCH(1,1) Model", xaxt = "n")
lines(sGARCH_dlr_ICs[2, ], type = "b", pch = 16, col = "firebrick")
lines(allGARCH_dlr_ICs[3, ], type = "b", pch = 16, col = "mediumseagreen")
lines(allGARCH_dlr_ICs[4,], type = "b", pch = 16, col = "powderblue")
lines(allGARCH_dlr_ICs[5,], type = "b", pch = 16, col = "palegreen")
lines(allGARCH_dlr_ICs[6,], type = "b", pch = 16, col = "pink")
lines(allGARCH_dlr_ICs[7,], type = "b", pch = 16, col = "orchid")
lines(allGARCH_dlr_ICs[8,], type = "b", pch = 16, col = "lightsalmon")
lines(allGARCH_dlr_ICs[9,], type = "b", pch = 16, col = "royalblue")
lines(allGARCH_dlr_ICs[10,], type = "b", pch = 16, col = "lightslategrey")
lines(allGARCH_dlr_ICs[11,], type = "b", pch = 16, col = "palevioletred")
lines(allGARCH_dlr_ICs[12,], type = "b", pch = 16, col = "gold")
axis(1, at = 1:length(allGARCH_dlr_ICs[1,]), labels = x_label, tick = FALSE)

# Set the coordinates for the legend outside the plot
legend_x <- length(allGARCH_dlr_ICs[1,]) + 0.3
legend_y <- mean(range(allGARCH_dlr_ICs)) +0.033

# Add a legend outside the plot
legend(legend_x, legend_y, legend = c("ARMA(0,0)+sGARCH(1,1)", "ARMA(0,4)+sGARCH(1,1)", "ARMA(2,2)+sGARCH(1,1)", "ARMA(5,0)+sGARCH(1,1)","ARMA(0,0)+eGARCH(1,1)","ARMA(0,4)+eGARCH(1,1)","ARMA(2,2)+eGARCH(1,1)","ARMA(5,0)+eGARCH(1,1)","ARMA(0,0)+iGARCH(1,1)","ARMA(0,4)+iGARCH(1,1)","ARMA(2,2)+iGARCH(1,1)","ARMA(5,0)+iGARCH(1,1)"), col = c("burlywood", "firebrick", "mediumseagreen", "powderblue","palegreen","pink","orchid","lightsalmon","royalblue","lightslategrey","palevioletred","gold"), pch = 16, xpd = TRUE, horiz = FALSE)

```
```{r l, include=TRUE}
daily_data_all <- daily[1:2466,c(1,6)]

d_return_all <- data.frame(Date = daily_data_all[,1][-1], return = diff(daily_data_all[,2])/ daily_data_all[-
dim(daily_data_all)[1], 2]) 

d_lreturn_all <- data.frame(Date = daily_data_all[,1][-1], logreturn = log(d_return_all[,2] + 1))

d_return_all$return <- 100 * d_return_all$return # 乘以100(%)作为分析数据
d_lreturn_all$logreturn <- 100 * d_lreturn_all$logreturn # 乘以100(%)作为分析数据

plot(d_lreturn_all$logreturn,type="l")

fit1_all <- ugarchfit(ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(11, 0)),
  distribution.model = "std"), data = d_lreturn_all[,2])
```

```{r l, include=TRUE}
# Out-Sample Forecasting
forecasts <- ugarchforecast(fit9_a, n.ahead = 10)
point_forecasts <- as.numeric(forecasts@forecast$seriesFor)

forecasts_all <- ugarchforecast(fit1_all, n.ahead = 10)
point_forecasts_all <- as.numeric(forecasts_all@forecast$seriesFor)

fore_price <- daily_data[941,2] * exp(cumsum(point_forecasts/100))
fore_price_all <- daily_data[941,2] * exp(cumsum(point_forecasts_all/100))

plot.new()
plot(1:50,c(daily_data[902:941,2], fore_price),  
      type="l", ylab="", xlab="", ylim = c(35, 46),main="Forecasting of stock price")
lines(40:50, append(daily_data[941,2], fore_price), type="l", col="red")
lines(40:50, append(daily_data[941,2], fore_price_all), type="l", col="darkgreen")
legend(x = "topright", c( "ARMA(0,0)+iGARCH(1,1)","ARMA(11,0)+iGARCH(1,1)"), lty=c(1,1), pch=".", 
       col=c("red","darkgreen"))
```
